Davos: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2023-09-22 paper/main.tex
expanded start of top-level functions section slightly

The Davos package also provides a handful of top-level functions for convenience and to provide additional functionality:

>>>>

The Davos package also provides a handful of functions available in the top-level \texttt{davos} namespace. Some of these function serve primarily as conveniences, while others provide additional functionality:
